Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-27 docs/papers/roofline_model/gocean_roofline.tex
roofline: add some description of the daxpy kernels.

>>>>

As well as examining the performance of the Continuity kernel, we have
also experimented with altering the DAXPY kernel of the STREAM2
benchmark so as to vary its $AI$. We did this by adding further
arithmetic operations but making use of the same array
elements. We used four different kernels:
\begin{enumerate}
\item {\tt b(i) = b(i) + scalar*a(i)}
\item {\tt b(i) = b(i) + scalar*a(i)+ a(i)*b(i)}
\item {\tt b(i) = b(i) + scalar*a(i)+ a(i)*b(i)*b(i)}
\item {\tt b(i) = b(i) + scalar*a(i)+ a(i)*b(i)*b(i)*b(i)}
\end{enumerate}
Figure~\ref{FIG_daxpy_roofline} shows the performance of these kernels
on a roofline plot for the E5-1620 CPU. They generally reach L2 and L3
bandwidth apart from at the lowest AI. Continuity kernel has AI of
{\bf xxx more discussion here}
